% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
\experience
  {Present}  {Software Engineer}{Episerver}{Viet Nam}
  {Aug 2018}  {  
Episerver Personalization is an intelligent personalization suite of products available in the cloud with a simple SaaS subscription. By combining machine learning, artificial intelligence, and statistical analysis, it empowers merchandisers to present individualized content and product selections in multiple channels, without complicated configuration. The platform conceptualizes a traditional Data Management Platform (DMP), while offering advanced personalization tools and a secure and compliant user interface to enable your customers to control their presences - even the right to be forgotten.\\
As a software engineer, I do following tasks on my daily working:
	\begin{itemize}
        \item Develop new features and functionality in Java for the existing as well as new products and services.       
        \item Investigate new technology and create prototypes sometime.                         
        \item Develop robust and well documented code that adheres to the team’s coding practices and standards.
        \item Adhere to TDD and agile practices and proactively communicate progress and/or issues.       
        \item Collaborate with core team in UK and teams based in the Stockholm and Hanoi to deliver global company road-map objectives.        
        \item Maintain existing code base and work on technical debt and support issues.
        \item Learn Scala on the job and develop skills to support and write new features and functionality in Scala.
	\end{itemize}
}
{Agile/Scrum,Java-8,Scala,JUnit 4.x,SpringMVC 4.x,Hibernate 4.x,Microsoft SQL server,My SQL,Apache Cassandra,Maven,Git,Jira,Jenkins,IntelliJ,Upsource}
\emptySeparator

\experience
  {Aug 2018}  {Technical Leader}{Pentalog}{Viet Nam}
  {Oct 2017}  {  
Rebuild ART application from scratch to doesn't only upgrade ART from “Recipe Repository” to “Recipe Development Tool”  but achieve new front-end design (UI/UX), application performance and db modeling correction.\\
For this project, I am the Technical Leader from Pentalog side. Basically my responsibilities are:
	\begin{itemize}
        \item At beginning phase of the project: did some technical POCs to prove right front-end technologies selection.       
        \item Consult Givaudan to select right technical redesign approach.                         
        \item Modeling and redesign DB (correction old db modeling) and migrate PDM from Oracle to PostgreSQL.
        \item Set-up back-end architecture for the project to satisfy Givaudan’s development standards based on Java-8, Maven, SpringBoot, Spring MVC, Springfox.       
        \item Working with Singapore Givaudan ART team as a technical contact point.        
        \item Take care of the technical aspects of the project.
        \item Involve to implement some API at back-end.
	\end{itemize}
}
{Agile/Scrum,Vue.js,Vuetify.js,Stylus,RxJS,Java-8,SpringMVC 4.x,Springfox,Spring Boot 1.x,JPA 2.1/Hibernate 5.x,PostgreSQL 10.3,Jasper Report,Mockito 1.9.5,JUnit,Apache Ant,Maven,Git,Jira,Jenkins,Sonar,IntelliJ,SoapUI}
\emptySeparator

\experience
  {Apr 2017}  {Senior Java Developer}{Pentalog}{Viet Nam}
  {Mar 2016}  {  
ART (Application Recipe Tool) helps to manage recipes, ingredients and flavors. When a client feels something and gives us description. The description will be passed to the application in form of plain text.\\
The job of the whole application is to figure out the appropriate recipe along with ingredients then give it back to the client. In short, if customer wants a flavor, the application will come up with the expected flavor as fast as possible.
	\begin{itemize}
        \item Bug fixing.       
        \item Refactoring legacy code.                          
        \item Communicate with client directly via skype or tele-conference to collect and clarify business requirements.
        \item Implement feature both client side and server side + unit test.       
        \item In charge of solving difficult issues: architecture design, performance benchmark, etc.                          
	\end{itemize}
}
{Agile/Scrum,Jquery 1.11,Bootstrap 3,Underscore 1.4.4,J2SE6,SpringMVC 4.x,JPA/Hibernate 4.x,Oracle 11.2,JXLS 2.3.0,Mockito 1.9.5,JUnit 4.11,Gson,Apache Ant,Gradle,Git,Jira,Jenkins,Sonar,IntelliJ,SoapUI}
\emptySeparator

\experience
  {Feb 2016}  {Senior Java Developer}{Pentalog}{Viet Nam}
  {Sep 2015}  {  
Pentalog Java team works on the corrective and evolutive maintenance of part of the client’s information system which includes several services:\\
- Parental control: API development for a parental control solution.\\
- Hosting management, CMS and domain names: API development for services networks.\\
- Migration from Domino: replacement of Domino features towards Java, Jboss, MySQL etc.\\
[0.2 cm]
Development full-flow  feature:
	\begin{itemize}
        \item Communicate with client directly via skype or tele-conference to collect and clarify business requirements.       
        \item Implement feature both client side and server side + unit test.                          
	\end{itemize}
}
{Agile/Scrum,J2SE 6,Jboss,MySQL 5.x,Apache CXF,Spring 3.x,JPA/Hibernate 3.x, Maven 2}
\emptySeparator

\experience
  {Jul 2015}  {Java Technical Leader}{Pentalog}{Viet Nam}
  {Dec 2012}  {  
The ISource project aims at providing a solution intended for all the actors involved in the company's sourcing process, through an application composed of two parts: mobile and web. The mobile part allows field buyers to collect information about suppliers and manage deals, while the warehouse managers and accountants can access it to update the status of the closed deals and report payment once the delivery has been made. The web part is addressed to the sourcing managers and the category managers supporting them in following up the sourcing activity and setting goals to field buyers, through different dashboards and reports.
\vspace{2mm}
The project had 2 phases with below timing:\\
ISource-2: Sep 2014 - Jul 2015\\
ISource-1: Dec 2012 - Dec 2013
\vspace{2mm}
	\begin{itemize}
        \item Creation of the server-side architecture (REST Web Services).       
        \item Documentation of the server-side architecture.                       \item Coding of the functions and creation of unit tests for whole server-side of the application.
        \item Coding of some functions on the client-side with Backbones, jQuery Mobile, jQgrid mobile.        
	\end{itemize}
}
{Agile/Scrum,Require.js,Underscore 1.4.4,BackBone 1.0,jqGrid mobile 1.1,Jquery mobile 1.3.2,JXLS 1.0.2,Gson,ModelMapper,JPA/Hibernate 4,REST/Jersey 1.x,Spring 4.x,J2SE6,Mockito 1.9.5,JUnit 4.11,Jira,Hudson,Sonar,Eclipse STS}
\emptySeparator

\experience
  {Jul 2012}  {Senior Java Developer}{Pentalog}{Viet Nam}
  {Feb 2012}   {
Senior Developer within a project concerning the development of a web-based application that enables clients to access online insurance product catalogs, to compare and to check product availability.\\
The application allows brokers to manage their sale strategies and claims from their clients.
	\begin{itemize}
        \item Code and product design.       
        \item Creation of estimations.                 
        \item Implementation of new modules for the product.
        \item In charge of solving difficult technical issues.
        \item Writing of the code and unit tests.
	\end{itemize}
}
{Agile/Scrum,CSS,XHTML,jQuery,JSF/PrimeFaces,Spring,JPA/Hibernate,MySQL,Apache Tomcat,Maven,SVN,Eclipse}
\emptySeparator

\experience
  {Dec 2011}  {Technical Leader}{FPT Software}{Viet Nam}
  {Sep 2011}   {
Technical Leader within the SERVICE-Broker project, developed for ServicePower.\\
The application was created to ensure that the incoming requests were correctly forwarded to other services, in the appropriate order, based on the configuration set up, and that the responses were properly dealt with. The application acts as a forwarding agent between the three parties: customer calling service, SERVICE-Scheduling system and SERVICE-Dispatch system.
	\begin{itemize}
        \item Creation of the application framework.       
        \item Responsible for solving difficult technical issues.                 \item In charge of suggesting technology.
        \item Writing of the code and unit tests.
	\end{itemize}
}
{Agile/Scrum,SoapUI,Apache Tomcat,CVS,Eclipse,SQL Server 2008,Apache AXIS 1.x,Spring,JPA/Hibernate}
\emptySeparator

\experience
  {Jul 2011}  {Technical Leader}{FPT Software}{Viet Nam}
  {Mar 2011}   {
Technical Leader within a development project of the Crawler and Reporting Tool - tools for validating portal pages, created for Net – Mobile AG, Germany.
	\begin{itemize}
        \item Creation of the application framework.       
        \item Responsible for solving difficult technical issues.                 \item In charge of suggesting technology.
        \item Writing of the code and unit tests.
	\end{itemize}
}
{Agile/Scrum,JasperReports,PostGreSQL,Smart GWT,GWT,JPA/Hibernate,Spring, Swing,JavaScript,J2SE 6}
\emptySeparator

\experience
  {Mar 2011}  {Senior Java Developer}{FPT Software}{Viet Nam}
  {Jan 2011}   {
Senior Developer within the JP-TPA Project (Jurong Port – Trailer Parking Application). The aim of the project was to enhance the Overnight Parking of Vehicle Application and the JP-Online Billing System.
	\begin{itemize}
        \item Creation of the detail design document.       
        \item Writing of the code and unit tests.           
        \item Helping junior member.
	\end{itemize}
}
{J2SE 5,JSP/Servlet,EJB,JDBC,CSS,HTML,JavaScript,Oracle DB,WebLogic,Eclipse,UML,StarUML,CVS,VSS,UML,StarUML}
\emptySeparator

\experience
  {Jan 2011}  {Senior Java Developer}{FPT Software}{Viet Nam}
  {Jul 2009}   {
Senior Developer within the HCVS project (Hitachi Capital Vehicle Solutions) for Harvey Nash, UK.\\
The objective of the project was to develop a web-based e-commerce application and data warehouse to supersede Capital Control and Online Quoting tool and retake the market lead.
	\begin{itemize}
        \item Analysis of the software requirements.       
        \item Writing of the technical documents.   
        \item Writing of the code and unit tests.
        \item Helping junior member.
	\end{itemize}
}
{J2SE 5,Struts 2,Spring 2.x,JPA/Hibernate3.x,CSS,HTML,JavaScript,jQuery,IText,Apache Poi,Oracle DB,Apache Tomcat, Maven,Eclipse,UML,StarUML,CVS,VSS}
\emptySeparator

\experience
  {Jul 2009}  {Java Developer}{IFI Solution}{Viet Nam}
  {Mar 2009}   {
Developer within the SINDOM 2 Project (Siemens IntraNet Database Operation Maintenance) for Onion (Italy) – a maintenance project of a 3-tier system, that manages network elements and interfaces between them in mobile network (for both 2G and 3G technology).
	\begin{itemize}
        \item Analysis of the software requirements.       
        \item Writing of the technical documents.   
        \item Maintenance of the code.        
	\end{itemize}
}
{Tortoise SVN,Jboss,Eclipse,UML,StarUML,Oracle,Web Services,EJB,J2SE 5,J2EE 4,XSL/XPATH}
\emptySeparator

\experience
  {Feb 2009}  {Java Team leader}{IFI Solution}{Viet Nam}
  {Nov 2008}   {
Team Leader within the IHM PAC (Human-Machine Interface for Production, Home and Consumption for EDELIA.\\
The website provides information about the heating service of each household and is part of the set service for electric-water-gas of EDF-ENR.
	\begin{itemize}
        \item Analysis of the software requirements.       
        \item Creation of the detail design document.   
        \item Coordination of the coding team.
        \item Writing of the code.
        \item In charge of fixing bugs.
	\end{itemize}
}
{J2SE 5,JSP/Servlet,HTML,CSS,Javascript,WebLogic,Web Services(SOAP),Struts 1,Hibernate,Oracle DB,Ant,Eclipse,UML,StarUML}
\emptySeparator

\experience
  {Sep 2008}  {Java Developer}{IFI Solution}{Viet Nam}
  {Mar 2008}   {
Developer within the DLD v200 and V210 Project for THALES avionic (DataLoaDer).\\
The DLD is a subsystem of CMS (Centralized Maintenance System). The aim of CMS is to help maintenance crew quickly isolate the failures and put back the aircraft in operational state.The DLD implements “upload of software and database” function and “Human Machine Interface” function of CMS.
	\begin{itemize}
        \item Analysis of the software requirements.       
        \item Writing of the IRS document.   
        \item Writing of the code and unit tests.
        \item In charge of running tests and solving bugs. 					\end{itemize}
}
{Rational Test Real Time,Eclipse, MS Visio, J2SE 5(Swing\cdot Socket\cdot Multi-threading),SQL/HSQL DB}
\emptySeparator

\experience
  {Jan 2008}  {Java Developer}{IFI Solution}{Viet Nam}
  {July 2007}   {
Developer within the CMI v210 (Centralized Maintenance Interface) Project for THALES Avionics.\\
The CMI is a subsystem of CMS (Centralized Maintenance System). The aim of CMS is to help maintenance crew quickly isolate failures and put back the aircraft in operational state. The CMI implements three functions of the CMS, namely: "report and elaboration", "interactive actions with MS (a subsystem on the aircraft)", "Human Machine Interface".
	\begin{itemize}
		\item Analysis of the software requirements.      
        \item Writing of the SDD document (including preliminary design and detail design).       
        \item Writing of the code and unit tests.         
        \item In charge of running tests and solving bugs.                      \end{itemize}                 
}
{Rational Test Real Time,Eclipse, MS Visio, J2SE 4(Swing\cdot Socket\cdot  Multi-threading),SQL/HSQL DB,UML,StarUML}

\end {experiences}